MS_Imp_Guidelines

### 2024-03-02 Markdown/Manuscript/Child_RMDs/MS_Body.Rmd
submission ready

@@

>>>>

**Key points for decision makers:**

-	How health economic models are implemented as software significantly shapes how easy they are to transfer to other decision contexts.

-	We have developed a software framework that can help implement a transparent, reusable and updatable economic model in youth mental health.

-	Our framework can be a prototype for software tools that improve the transferability of health economic models more generally.

@@

## Author contributions
MPH led the conceptualisation and software implementation of ready4 and readyforwhatsnext and manuscript drafting. MH, CG and GW co-authored the software described in this article. All co-authors critically reviewed and revised manuscript drafts and approved the final manuscript text.

### 2024-03-02 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
submission ready

As illustrated by Table \@ref(tab:checktb), we have developed a software framework and used it to author CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability. We have used toy data to demonstrate how these CHEM module libraries, originally developed for a single utility mapping study [@Hamilton2021.07.07.21260129], can be applied: (i) to datasets from new samples with different concepts and variable names; (ii) to construct models with different utility instruments, predictors and covariates; and (iii) to develop and use both cross-sectional and longitudinal mapping models.

@@

Factors such as <!-- user enjoyment,  -->usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development]. To systematically address these issues for our prototype software framework would require investments in engaging the health economic modelling community to refine framework user requirements, software re-development and testing to meet those requirements, integration with evolving code and documentation authoring capabilities of large language models, the development of improved and more comprehensive documentation and training resources and proactive user-community building and support. We currently lack the resources to undertake these tasks.

>>>>

We have developed a software framework and used it to author CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability. We have used toy data to demonstrate how these CHEM module libraries, originally developed for a single utility mapping study [@Hamilton2021.07.07.21260129], can be applied: (i) to datasets from new samples with different concepts and variable names; (ii) to construct models with different utility instruments, predictors and covariates; and (iii) to develop and use both cross-sectional and longitudinal mapping models.

@@

Factors such as <!-- user enjoyment,  -->usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development]. To systematically address these issues for our prototype would require investments in: (i) engaging the health economic modelling community in refining framework user requirements; (ii) undertaking software re-development and testing to meet those requirements: (iii) incoporating the evolving code and documentation authoring capabilities of large language models; (iv) the development of improved and more comprehensive documentation and training resources; and (v) proactive user-community building and support. We currently lack the resources to undertake these tasks.

### 2024-03-02 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
submission ready

## Transferability
We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia. Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks. <!-- Promoting mentally healthy local communities is also an important role for Australian local governments. -->The mental health of young people is a global priority [@https://doi.org/10.1002/wps.20938] and Australia has initiated youth mental health service model reforms that have been adopted in other jurisdictions [@RN27]. For these reasons, we aim to develop readyforwhatsnext in a manner that facilitates its transfer to multiple decision contexts.

@@

To meet these criteria we are implementing readyforwhatsnext as an open-source, modular model. Open source projects grant third parties permissions to access, use and modify model source code and data. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. <!-- Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. -->When undertaking analyses intended to inform decision-making, readyforwhatsnext uses real Australian data (which can be empirical, simulated or assumption-based). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are creating toy datasets. <!-- PHNS -->A high-level schematic guiding our implementation of readyforwhatsnext is outlined in Figure \@ref(fig:fig1).

>>>>

## Transferability
We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia. Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent, regionally focused organisations called Primary Health Networks. <!-- Promoting mentally healthy local communities is also an important role for Australian local governments. -->The mental health of young people is a global priority [@https://doi.org/10.1002/wps.20938] and Australia has initiated youth mental health service model reforms that have been adopted in other jurisdictions [@RN27]. For these reasons, we aim to develop readyforwhatsnext in a manner that facilitates its transfer to multiple decision contexts.

@@

To meet these criteria we are implementing readyforwhatsnext as an open-source, modular model. Open source projects grant third parties permissions to access, use and modify model source code and data. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. <!-- Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. -->When undertaking analyses intended to inform decision-making, readyforwhatsnext uses real Australian data (which can be empirical, simulated or assumption-based). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are creating synthetic or toy datasets ("fake" data that realistically represent the key features of observed data, but which can be shared without confidentiality concerns  [@bellovin2019privacy]). <!-- PHNS -->A high-level schematic guiding our implementation of readyforwhatsnext is outlined in Figure \@ref(fig:fig1).
